Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-06-26 tensor/draft/draft-tensor-op.tex
[plot,tensor] Replace scSP plots in draft
* contour_two accepts linestyle
* each scenario gets different linestyle

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
  \caption{
    \eos{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green)
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson[NP]{10} \in [-1,\, 9]$, $\wilson[NP]{10'} \in [-5,\,5]$ (red)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
    }
  }
  \label{fig:scalar}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,2}
%  \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \caption{
    \eos{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green)
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson[NP]{10} \in [-1,\, 9]$, $\wilson[NP]{10'} \in [-5,\,5]$ (red)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
    }
  }
  \label{fig:scalar}
\end{figure*}
